---
title: "autoCV"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{autoCV}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=TRUE}
library(autoCV)
```

# Set up data

## Get example data

```{r Get example data}
wd <- autoCV::get_data(save_dir = file.path(tempdir(),"example_data"))
### List all files, grouped by subfolder
autoCV::get_data_list(wd)
```

## Customise data

Now you may edit each file as needed to customise your CV. 
The subfolders are organised as follows:  

- `cv_data/` contains the data files for each section of the CV.
- `img/` contains any images you wish to include in the CV.
- `css/` contains the CSS file for styling the CV.


# Create CV

## Set up template

```{r Set up template}
file <- autoCV::get_template(wd = wd,
                             save_dir = tempdir(),
                             tagline = "Simplicity is the ultimate sophistication.",
                             extra = list("### Studio of Andrea del Verrocchio",
                                           "### Painter, Draughtsman, Engineer, Scientist",
                                           "### MD, PhD"),
                             logo = get_logo(img = system.file("img","davinci.png",
                                                               package = "autoCV"),
                                              width = "60px"),
                             force_new = TRUE
                             )
```

You can then inspect and make any further edits to the Rmarkdown file
by opening it with in RStudio with: `browseURL(file)`

```{r, eval=FALSE}
browseURL(file)
```


## Render as HTML

To generate the CV, render the template file with `render_cv`.

```{r Render template, eval=FALSE}
file_html <- autoCV::render_cv(file = file) 
```

You can then open the rendered HTML file in RStudio with: `browseURL(file_html)`

```{r, eval=FALSE}
browseURL(file_html)
```


## Render as PDF

To render the CV as a PDF instead, simply use the `as_pdf` argument.

```{r, eval=FALSE}
file_pdf <- autoCV::render_cv(file = file, 
                              as_pdf = TRUE) 
```


# Rendered examples

See here for an example of a rendered CV:  

## [HTML format](https://bschilder.github.io/CV/CV.html)
## [PDF format](https://bschilder.github.io/CV/CV.pdf)

# Session info

<details>
```{r}
utils::sessionInfo()
```
</details>

